---
title: "comparing algaen15-fishn15 with home ranges"
author: "CEB"
date: '2026-04-03'
output: html_document
---



#-----------checking relationship between turbinaria n15 and fish n15-----------------
 ##use turbinaria for surgeonfish - side of motu (because larger home range) - in old file already**
 ##for damselfish - only use closest 3 algae samples (because small home range, encompasses capture area)
 

##load packages
```{r}
library(tidyverse) #for everything

#for bayesian modelling and interpreting:
library(brms)
library(tidybayes)
library(emmeans)

```


#load data
```{r}

turb_23_gps_dat<-read.csv("../data/turb_gps_points.csv")
turb_23_dat<-read.csv("../data/turb_focal_isotopes_nov_2023.csv")


steg_23_dat<-read.csv("../data/stegastes_data.csv")%>%
  select(-X)


str(steg_23_dat)

```

#first need to combine Turbinaria data with info on side of motu and gps coords:
```{r}

turb_23_gps_dat2<-
  turb_23_gps_dat%>%
  rename(motu = Motu, 
         side = Side,
         waypoint = GPS_name)

turb_23_gps_dat2


turb_23_comb_dat<-
  left_join(turb_23_dat, turb_23_gps_dat2,
            by = join_by(motu, waypoint))
turb_23_comb_dat
#all good**


##get mean turb value per side - predictor 1
turb_23_mean_dat<-
  turb_23_comb_dat%>%
  group_by(motu, side)%>%
  summarize(mean_turb_n15 = mean(X15N))%>%
  ungroup()
turb_23_mean_dat

  turb_23_comb_dat%>%
  group_by(motu, side)%>%
  summarize(mean_turb_n15 = mean(X15N),
            count_n15 = length(X15N))%>%
  ungroup()

```

##get mean turb for closest 3 points
```{r}

#Aie	leeward		- 4, 5, 6	
#Aie	windward			- 1, 2, 9
#Reiono	leeward		- 35, 36, 37	
#Reiono	windward		- 94, 95, 97	
#Rimatuu	leeward	 -112, 113, 114		
#Rimatuu	windward	- 332, 342, 10

turb_23_mean_dat_for_steg<-
turb_23_comb_dat %>%
  filter(waypoint == 4|waypoint == 5|waypoint == 6|
           waypoint == 1|waypoint == 2|waypoint == 9|
           waypoint == 35|waypoint == 36|waypoint == 37|
           waypoint == 94|waypoint == 95|waypoint == 97|
           waypoint == 112|waypoint == 113|waypoint == 114|
           waypoint == 332|waypoint == 342|waypoint == 10)%>%
  group_by(motu, side)%>%
  summarize(mean_turb_n15 = mean(X15N),
            n_n15 = length(X15N))%>%
  ungroup()

turb_23_mean_dat_for_steg

#from here:
#Aie	leeward	10.903333	3	
#Aie	windward	9.606667	3	
#Reiono	leeward	14.013333	3	
#Reiono	windward	10.433333	3	
#Rimatuu	leeward	7.410000	3	
#Rimatuu	windward	15.466667	3	


#compare to above per side of motu: 
#Aie	leeward	10.746667		
#Aie	windward	9.606667		
#Reiono	leeward	14.063333		
#Reiono	windward	11.596667		
#Rimatuu	leeward	7.537857		
#Rimatuu	windward	15.476667	

#nearly identical....

cor.test(turb_23_mean_dat_for_steg$mean_turb_n15, turb_23_mean_dat$mean_turb_n15)
#cor  = 0.9866321

#so i think we're fine to just use side of motu for both species, since the values are nearly identical and nearly perfectly correlated**
```


