

#-----------checking relationship between turbinaria n15 and fish n15-----------------
 

##load packages
```{r}
library(tidyverse) #for everything

#for bayesian modelling and interpreting:
library(brms)
library(tidybayes)
library(emmeans)

```


#load data
```{r}

turb_23_gps_dat<-read.csv("../data/turb_gps_points.csv")
turb_23_dat<-read.csv("../data/turb_focal_isotopes_nov_2023.csv")


acan_23_dat<-read.csv("../data/acanthurus_data.csv")%>%
  select(-X)

steg_23_dat<-read.csv("../data/stegastes_data.csv")%>%
  select(-X)


str(turb_23_gps_dat)
str(turb_23_dat)
str(acan_23_dat)
str(steg_23_dat)

```

#first need to combine Turbinaria data with info on side of motu and gps coords:
```{r}

turb_23_gps_dat2<-
  turb_23_gps_dat%>%
  rename(motu = Motu, 
         side = Side,
         waypoint = GPS_name)

turb_23_gps_dat2


turb_23_comb_dat<-
  left_join(turb_23_dat, turb_23_gps_dat2,
            by = join_by(motu, waypoint))
turb_23_comb_dat
#all good**


##get mean turb value per side - predictor
turb_23_mean_dat<-
  turb_23_comb_dat%>%
  group_by(motu, side)%>%
  summarize(mean_turb_n15 = mean(X15N))%>%
  ungroup()
turb_23_mean_dat
```

#now combine turbinaria data with fish data:------
```{r}
str(acan_23_dat)
str(steg_23_dat)


turb_23_mean_dat2<-
  turb_23_mean_dat%>%
  rename(Motu = motu,
         Exposure = side)%>%
  mutate(Motu = str_to_upper(Motu))
turb_23_mean_dat2



acan_23_turb_dat<-
  left_join(acan_23_dat, turb_23_mean_dat2, by = join_by(Motu, Exposure))
acan_23_turb_dat



steg_23_turb_dat<-
  left_join(steg_23_dat, turb_23_mean_dat2, by = join_by(Motu, Exposure))
steg_23_turb_dat
#great!


#and stegastes no outlier-----
steg_23_turb_dat_no_out<-
  steg_23_turb_dat%>%
  filter(Muscle_N15<=14)
steg_23_turb_dat_no_out


##and acanthurus no outlier-----
acan_23_turb_dat_no_out<-
  acan_23_turb_dat%>%
     filter(Muscle_C<52)
acan_23_turb_dat_no_out


#(previously comapred outlier vs no outlier for all analyses)

```


###center data
```{r}
#center data-----
steg_23_turb_dat_no_out_c<-
  steg_23_turb_dat_no_out%>%
  mutate(mean_turb_n15_c = base::scale(mean_turb_n15, center = TRUE, scale = FALSE),
         TL_cm_c = base::scale(TL_cm, center = TRUE, scale = FALSE),
         log_Muscle_N15 = log(Muscle_N15),
         log_Poo_N15 = log(Poo_N15))

acan_23_turb_dat_no_out_c<-
  acan_23_turb_dat_no_out%>%
  mutate(mean_turb_n15_c = base::scale(mean_turb_n15, center = TRUE, scale = FALSE),
         TL_cm_c = base::scale(TL_cm, center = TRUE, scale = FALSE),
         log_Muscle_N15 = log(Muscle_N15),
         log_Poo_N15 = log(Poo_N15))

```


##run analysis: muscle n15
```{r}

##stegastes-----
steg_muscle_n15_turb_size_mod_c_no_out_nest <- brm(Muscle_N15  ~ mean_turb_n15_c + TL_cm_c + (1|Motu/Motu_Exposure),
                data=steg_23_turb_dat_no_out_c,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/steg_muscle_n15_turb_size_mod_c_no_out_nest") 
print(steg_muscle_n15_turb_size_mod_c_no_out_nest)
pp_check(steg_muscle_n15_turb_size_mod_c_no_out_nest)
plot(steg_muscle_n15_turb_size_mod_c_no_out_nest, ask = FALSE)
#looks good

hypothesis(steg_muscle_n15_turb_size_mod_c_no_out_nest, "mean_turb_n15_c>0") #>.99*


###acanthurus-----
acan_muscle_n15_turb_size_mod_c_no_out_nest <- brm(Muscle_N15  ~ mean_turb_n15_c + TL_cm_c + (1|Motu/Motu_Exposure),
                data=acan_23_turb_dat_no_out_c,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/acan_muscle_n15_turb_size_mod_c_no_out_nest")
print(acan_muscle_n15_turb_size_mod_c_no_out_nest)
pp_check(acan_muscle_n15_turb_size_mod_c_no_out_nest)
plot(acan_muscle_n15_turb_size_mod_c_no_out_nest, ask = FALSE)
#looks good

hypothesis(acan_muscle_n15_turb_size_mod_c_no_out_nest, "mean_turb_n15_c>0") #.99*


```

##repeat for fecal n15:------
```{r}

###stegastes-----
steg_poo_n15_turb_size_mod_c_no_out_nest <- brm(Poo_N15  ~ mean_turb_n15_c + TL_cm_c + (1|Motu/Motu_Exposure),
                data=steg_23_turb_dat_no_out_c,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/steg_poo_n15_turb_size_mod_c_no_out_nest") #worked
print(steg_poo_n15_turb_size_mod_c_no_out_nest)
pp_check(steg_poo_n15_turb_size_mod_c_no_out_nest)
plot(steg_poo_n15_turb_size_mod_c_no_out_nest, ask = FALSE)
#looks good

hypothesis(steg_poo_n15_turb_size_mod_c_no_out_nest, "mean_turb_n15_c>0") #.97*


###acanthurus-----
acan_poo_n15_turb_size_mod_c_no_out_nest <- brm(Poo_N15  ~ mean_turb_n15_c + TL_cm_c + (1|Motu/Motu_Exposure),
                data=acan_23_turb_dat_no_out_c,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/acan_poo_n15_turb_size_mod_c_no_out_nest") #1 divergent
print(acan_poo_n15_turb_size_mod_c_no_out_nest)
pp_check(acan_poo_n15_turb_size_mod_c_no_out_nest)
plot(acan_poo_n15_turb_size_mod_c_no_out_nest, ask = FALSE)
#looks good

hypothesis(acan_poo_n15_turb_size_mod_c_no_out_nest, "mean_turb_n15_c>0") #.99*


```



##compare some estimates:
```{r}
steg_poo_n15_turb_size_mod_c_no_out_nest%>%
  spread_draws(b_mean_turb_n15_c)%>%
  median_hdi(b_mean_turb_n15_c)
#0.3203171	-0.02837322	0.6172764	

acan_poo_n15_turb_size_mod_c_no_out_nest%>%
  spread_draws(b_mean_turb_n15_c)%>%
  median_hdi(b_mean_turb_n15_c)
#0.7746735	0.1474984	1.414003	

steg_muscle_n15_turb_size_mod_c_no_out_nest%>%
  spread_draws(b_mean_turb_n15_c)%>%
  median_hdi(b_mean_turb_n15_c)
#0.3656213	0.1607173	0.6091697	

acan_muscle_n15_turb_size_mod_c_no_out_nest%>%
  spread_draws(b_mean_turb_n15_c)%>%
  median_hdi(b_mean_turb_n15_c)
#0.6896479	0.1422835	1.231588	

```



####model plots------
```{r}

##plots: best fit lines + raw data-----
#----Poo N15--------
steg_poo_n15_turb_me<-conditional_effects(steg_poo_n15_turb_size_mod_c_no_out_nest, effects = "mean_turb_n15_c", plot = FALSE, re_formula = NULL, prob = 0.85)[[1]]

mean(steg_23_turb_dat_no_out_c$mean_turb_n15) #12.32394


steg_poo_n15_turb_me_unscale<-
  steg_poo_n15_turb_me%>%
  mutate(mean_turb_n15 = mean_turb_n15_c +12.32394)


acan_poo_n15_turb_me<-conditional_effects(acan_poo_n15_turb_size_mod_c_no_out_nest, effects = "mean_turb_n15_c", plot = FALSE, re_formula = NULL, prob = 0.85)[[1]]

mean(acan_23_turb_dat_no_out_c$mean_turb_n15) #11.6554

acan_poo_n15_turb_me_unscale<-
  acan_poo_n15_turb_me%>%
  mutate(mean_turb_n15 = mean_turb_n15_c +11.6554)


poo_colors <- c("Damselfish" = "#332288", "Surgeonfish" = "#88CCEE")
shape<-c("Damselfish" = 19, "Surgeonfish" = 17)


poo_n15_turb_plot<-
steg_23_turb_dat_no_out_c%>%
  ggplot(aes(x = mean_turb_n15, y = Poo_N15))+
   geom_ribbon(data = steg_poo_n15_turb_me_unscale, aes(y = estimate__,  ymin = lower__, ymax=upper__), alpha = .2, fill = "#332288")+
   geom_line(data = steg_poo_n15_turb_me_unscale, aes(y = estimate__), color = "#332288", alpha = .9, lwd = 1) +
     geom_ribbon(data = acan_poo_n15_turb_me_unscale, aes(y = estimate__,  ymin = lower__, ymax=upper__), alpha = .2, fill = "#88CCEE")+
   geom_line(data = acan_poo_n15_turb_me_unscale, aes(y = estimate__), color = "#88CCEE", alpha = .9, lwd = 1) +
  geom_point(data = acan_23_turb_dat_no_out_c, aes(pch = "Surgeonfish", color = "Surgeonfish"), size = 2)+
  geom_point(aes(pch = "Damselfish", color = "Damselfish"), size = 2)+
  scale_color_manual(values = poo_colors, name = "")+
    scale_shape_manual(values = shape, name = "")+
    ylab(expression(Fecal~italic(delta)^15*N)) +
      xlab(expression(Nearshore~seabird~nutrients~(algal~italic(delta)^15*N))) +
  scale_y_continuous(limits = c(0,15), breaks = c(0, 5, 10, 15))+ #match other plots
 # scale_fill_manual(values = colors)+
  theme_bw() +
   theme(element_text(size = 12),
         panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.position = "inside",
       # legend.position.inside = c(.8, .2),
       legend.position.inside = c(.3, .88))
poo_n15_turb_plot



#----muscle N15--------
steg_muscle_n15_turb_me<-conditional_effects(steg_muscle_n15_turb_size_mod_c_no_out_nest, effects = "mean_turb_n15_c", plot = FALSE, re_formula = NULL, prob = 0.85)[[1]]

mean(steg_23_turb_dat_no_out_c$mean_turb_n15) #12.32394


steg_muscle_n15_turb_me_unscale<-
  steg_muscle_n15_turb_me%>%
  mutate(mean_turb_n15 = mean_turb_n15_c +12.32394)


acan_muscle_n15_turb_me<-conditional_effects(acan_muscle_n15_turb_size_mod_c_no_out_nest, effects = "mean_turb_n15_c", plot = FALSE, re_formula = NULL, prob = 0.85)[[1]]

mean(acan_23_turb_dat_no_out_c$mean_turb_n15) #11.6554

acan_muscle_n15_turb_me_unscale<-
  acan_muscle_n15_turb_me%>%
  mutate(mean_turb_n15 = mean_turb_n15_c +11.6554)


muscle_colors <- c("Damselfish" = "#117733", "Surgeonfish" = "#44AA99")
shape<-c("Damselfish" = 19, "Surgeonfish" = 17)

muscle_n15_turb_plot<-
steg_23_turb_dat_no_out_c%>%
  ggplot(aes(x = mean_turb_n15, y = Muscle_N15))+
   geom_ribbon(data = steg_muscle_n15_turb_me_unscale, aes(y = estimate__,  ymin = lower__, ymax=upper__), alpha = .2, fill = "#117733")+
   geom_line(data = steg_muscle_n15_turb_me_unscale, aes(y = estimate__), color = "#117733", alpha = .9, lwd = 1) +
     geom_ribbon(data = acan_muscle_n15_turb_me_unscale, aes(y = estimate__,  ymin = lower__, ymax=upper__), alpha = .2, fill = "#44AA99")+
   geom_line(data = acan_muscle_n15_turb_me_unscale, aes(y = estimate__), color = "#44AA99", alpha = .9, lwd = 1) +
  geom_point(data = acan_23_turb_dat_no_out_c, aes(pch = "Surgeonfish", color = "Surgeonfish"), size = 2)+
  geom_point(aes(pch = "Damselfish", color = "Damselfish"), size = 2)+
 # geom_jitter(data = acan_23_turb_dat_c, width = 0.4, height = 0, aes(pch = "Surgeonfish", color = "Surgeonfish"))+
   # geom_jitter(width = 0.4, height = 0, aes(pch = "Damselfish", color = "Damselfish"))+
  scale_color_manual(values = muscle_colors, name = "")+
    scale_shape_manual(values = shape, name = "")+
    ylab(expression(Muscle~italic(delta)^15*N)) +
      xlab(expression(Nearshore~seabird~nutrients~(algal~italic(delta)^15*N))) +
    scale_y_continuous(breaks = c(4, 8, 12, 16), limits = c(3, 17))+
 # scale_fill_manual(values = colors)+
  theme_bw() +
   theme(element_text(size = 12),
         panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.background = element_blank(),
        legend.title = element_blank(),
        legend.position = "inside",
        #legend.position.inside = c(.8, .2),
                legend.position.inside = c(.3, .88))
muscle_n15_turb_plot



##plots: posterior distns:-----
#plot stegastes and acanthurus together------
muscle_turb_posterior_plot<-
ggplot() +
   geom_vline(xintercept=0, lty=2, alpha = .5)+
###Posterior densities for stegastes - n15 
  stat_halfeye(data = as_draws_df(steg_muscle_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1.1, fill = "Damselfish", color = "Damselfish", pch = "Damselfish"), 
               point_interval=NULL, slab_alpha = .3) + 
  ##posterior densites for Atri:
  stat_halfeye(data = as_draws_df(acan_muscle_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1, fill = "Surgeonfish", color = "Surgeonfish", pch = "Surgeonfish"), 
                point_interval=NULL, slab_alpha = .3) + 
  
    scale_fill_manual(values = muscle_colors, name = "")+
  scale_color_manual(values = muscle_colors, name = "")+
  
  new_scale_color()+
  new_scale_fill()+
  
  ###outlines for stegastes - n15 
  stat_halfeye(data = as_draws_df(steg_muscle_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1.1, fill = "Damselfish", color = "Damselfish", pch = "Damselfish"),  point_interval = NULL,  slab_fill = NA, outline_bars = TRUE, slab_color = "#117733",   slab_linewidth = .5 ) + 
  ##outlinesfor Atri:
  stat_halfeye(data = as_draws_df(acan_muscle_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1, fill = "Surgeonfish", color = "Surgeonfish", pch = "Surgeonfish"),  point_interval = NULL,  slab_fill = NA, outline_bars = TRUE, slab_color = "#44AA99",   slab_linewidth = .5) + 
  
  
    ###point interval for stegastes - n15 
  stat_halfeye(data = as_draws_df(steg_muscle_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1.1, fill = "Damselfish", color = "Damselfish", pch = "Damselfish"), 
               point_interval=median_hdi, .width=c(.85,.5),  slab_fill = NA,  point_size = 2) + 
  ##point interval  for  Atri:
  stat_halfeye(data = as_draws_df(acan_muscle_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1, fill = "Surgeonfish", color = "Surgeonfish", pch = "Surgeonfish"),   point_interval=median_hdi, .width=c(.85,.5),  slab_fill = NA, pch = 17,  point_size = 2) + 
  
  
  
#now set formatting:
  scale_y_continuous(breaks = NULL)+
  scale_fill_manual(values = muscle_colors, name = "", guide = "none")+
  scale_color_manual(values = muscle_colors, name = "", guide = "none")+
      scale_shape_manual(values = shape, name = "")+
  ylab("")+
       scale_x_continuous(limits = c(-1, 2.5))+
 # xlab(expression(Posterior~effect~of~macroalgal~italic(delta)^15*N~on~muscle~italic(delta)^15*N)) +
 xlab("")+
 theme_bw() +
   theme(element_text(size = 12),
         legend.background = element_blank(),
         panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
                plot.background = element_blank(),
       # legend.position = c(.8, .8),
        legend.position = "none")
 muscle_turb_posterior_plot 
  
 
 
 poo_turb_posterior_plot<-
ggplot() +
   geom_vline(xintercept=0, lty=2, alpha = .5)+
###Posterior densities for stegastes - n15 
  stat_halfeye(data = as_draws_df(steg_poo_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1.1, fill = "Damselfish", color = "Damselfish", pch = "Damselfish"), 
               point_interval=NULL, slab_alpha = .3) + 
  ##posterior densites for Atri:
  stat_halfeye(data = as_draws_df(acan_poo_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1, fill = "Surgeonfish", color = "Surgeonfish", pch = "Surgeonfish"), 
                point_interval=NULL, slab_alpha = .5) + 
  
    scale_fill_manual(values = poo_colors, name = "")+
  scale_color_manual(values = poo_colors, name = "")+
  
  new_scale_color()+
  new_scale_fill()+
  
  ###outlines for stegastes - n15 
  stat_halfeye(data = as_draws_df(steg_poo_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1.1, fill = "Damselfish", color = "Damselfish", pch = "Damselfish"),  point_interval = NULL,  slab_fill = NA, outline_bars = TRUE, slab_color = "#332288",   slab_linewidth = .5 ) + 
  ##outlinesfor Atri:
  stat_halfeye(data = as_draws_df(acan_poo_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1, fill = "Surgeonfish", color = "Surgeonfish", pch = "Surgeonfish"),  point_interval = NULL,  slab_fill = NA, outline_bars = TRUE, slab_color = "#88CCEE",   slab_linewidth = .5) + 
  
  
    ###point interval for stegastes - n15 
  stat_halfeye(data = as_draws_df(steg_poo_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1.1, fill = "Damselfish", color = "Damselfish", pch = "Damselfish"), 
               point_interval=median_hdi, .width=c(.85,.5),  slab_fill = NA, point_size = 2) + 
  ##point interval  for  Atri:
  stat_halfeye(data = as_draws_df(acan_poo_n15_turb_size_mod_c_no_out_nest), aes(x = b_mean_turb_n15_c,  y = 1, fill = "Surgeonfish", color = "Surgeonfish", pch = "Surgeonfish"),   point_interval=median_hdi, .width=c(.85,.5),  slab_fill = NA, pch = 17, point_size = 2) + 
  
  
  
#now set formatting:
  scale_y_continuous(breaks = NULL)+
  scale_fill_manual(values = poo_colors, name = "", guide = "none")+
  scale_color_manual(values = poo_colors, name = "", guide = "none")+
      scale_shape_manual(values = shape, name = "")+
  ylab("")+
       scale_x_continuous(limits = c(-1, 2.5))+
 # xlab(expression(Posterior~effect~of~macroalgal~italic(delta)^15*N~on~poo~italic(delta)^15*N)) +
 xlab("")+
 theme_bw() +
   theme(element_text(size = 12),
         legend.background = element_blank(),
         panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
                plot.background = element_blank(),
       # legend.position = c(.8, .8),
        legend.position = "none")
 poo_turb_posterior_plot 
  


#now combine with posterior plots, too:-----
muscle_n15_turb_plot_inset <-
  ggdraw() +
  draw_plot(muscle_n15_turb_plot) +
  draw_plot(muscle_turb_posterior_plot, x = 0.5, y = .08,  width = .45, height = .35) #x = 0.11, y = .64,
muscle_n15_turb_plot_inset



poo_n15_turb_plot_inset <-
  ggdraw() +
  draw_plot(poo_n15_turb_plot) +
  draw_plot(poo_turb_posterior_plot,  x = 0.5, y = .08, width = .45, height = .35)
poo_n15_turb_plot_inset


n15_versus_turb_plots_with_pp_insets<-plot_grid(muscle_n15_turb_plot_inset, poo_n15_turb_plot_inset,
                                       ncol = 2)
n15_versus_turb_plots_with_pp_insets

```


###combine with seabird plots and save-----
```{r}
#from other datafile:
n15_versus_turb_plots_with_pp_insets
n15_versus_logsb_plots_with_pp_insets



n15_versus_turb_sb_plots_with_pp_insets<-plot_grid(muscle_n15_logsb_plot_inset, poo_n15_logsb_plot_inset, muscle_n15_turb_plot_inset, poo_n15_turb_plot_inset, 
                                       ncol = 2, labels = c("(a)", "(b)", "(c)", "(d)"), label_fontface = "plain", label_x = .14, label_y = 0.98, align = "hv")
n15_versus_turb_sb_plots_with_pp_insets


#ggsave(plot = n15_versus_turb_sb_plots_with_pp_insets, filename = "../outputs/figures/figure1.tif", 
 #      width  = 1961, height = 2000, units = "px")

```



###-----------FECAL N15~MUSCLE N15--------------
```{r}
acan_23_turb_dat_no_out_c2<-
  acan_23_turb_dat_no_out_c%>%
  mutate(Muscle_N15_c = base::scale(Muscle_N15, scale = FALSE, center = TRUE))

steg_23_turb_dat_no_out_c2<-
  steg_23_turb_dat_no_out_c%>%
  mutate(Muscle_N15_c = base::scale(Muscle_N15, scale = FALSE, center = TRUE))

acan_poo_muscle_n15_size_mod_c_no_out_nest <- brm(Poo_N15  ~ Muscle_N15_c + TL_cm_c + (1|Motu/Motu_Exposure),
                data=acan_23_turb_dat_no_out_c2,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/acan_poo_muscle_n15_size_mod_c_no_out_nest") #worked
print(acan_poo_muscle_n15_size_mod_c_nest)
pp_check(acan_poo_muscle_n15_size_mod_c_nest)
plot(acan_poo_muscle_n15_size_mod_c_nest, ask  = FALSE)
#looks good 

hypothesis(acan_poo_muscle_n15_size_mod_c_nest, "Muscle_N15_c>0") #1*****


steg_poo_muscle_n15_size_mod_c_no_out_nest <- brm(Poo_N15  ~ Muscle_N15_c + TL_cm_c + (1|Motu/Motu_Exposure),
                data=steg_23_turb_dat_no_out_c2,
              iter = 3000, warmup = 1000, cores=4, chains = 4, 
                  control = list(adapt_delta = 0.999, max_treedepth=15), 
                file = "../outputs/brms/steg_poo_muscle_n15_size_mod_c_no_out_nest") 
print(steg_poo_muscle_n15_size_mod_c_no_out_nest)
pp_check(steg_poo_muscle_n15_size_mod_c_no_out_nest)
plot(steg_poo_muscle_n15_size_mod_c_no_out_nest, ask = FALSE)
#looks good

hypothesis(steg_poo_muscle_n15_size_mod_c_no_out_nest, "Muscle_N15_c>0") #1**

```


##extract some model estimates-----
```{r}
acan_poo_muscle_n15_size_mod_c_no_out_nest%>%
  spread_draws(b_Muscle_N15_c)%>%
  median_hdi()
#0.6777382	0.423193	0.9746445	


steg_poo_muscle_n15_size_mod_c_no_out_nest%>%
 spread_draws(b_Muscle_N15_c)%>%
  median_hdi()
#1.112569	0.7331059	1.460298

```


###plot fecal n15~muscle n15
```{r}
##line plot-----
steg_poo_muscle_n15_me<-conditional_effects(steg_poo_muscle_n15_size_mod_c_no_out_nest, effects = "Muscle_N15_c", plot = FALSE)[[1]]

mean(steg_23_turb_dat_no_out_c2$Muscle_N15) #10.50792


steg_poo_muscle_n15_me_unscale<-
  steg_poo_muscle_n15_me%>%
  mutate(Muscle_N15 = Muscle_N15_c +10.50792)


acan_poo_muscle_n15_me<-conditional_effects(acan_poo_muscle_n15_size_mod_c_no_out_nest, effects = "Muscle_N15_c", plot = FALSE)[[1]]

mean(acan_23_turb_dat_no_out_c2$Muscle_N15) #10.45675

acan_poo_muscle_n15_me_unscale<-
  acan_poo_muscle_n15_me%>%
  mutate(Muscle_N15 = Muscle_N15_c +10.45675)


poo_colors <- c("Damselfish" = "#332288", "Surgeonfish" = "#88CCEE")
shape<-c("Damselfish" = 19, "Surgeonfish" = 17)

poo_muscle_n15_plot<-
steg_23_turb_dat_no_out_c2%>%
  ggplot(aes(x = Muscle_N15, y = Poo_N15))+
   geom_ribbon(data = steg_poo_muscle_n15_me_unscale, aes(y = estimate__,  ymin = lower__, ymax=upper__), alpha = .2, fill = "#332288")+
   geom_line(data = steg_poo_muscle_n15_me_unscale, aes(y = estimate__), color = "#332288", alpha = .9, lwd = 1) +
     geom_ribbon(data = acan_poo_muscle_n15_me_unscale, aes(y = estimate__,  ymin = lower__, ymax=upper__), alpha = .2, fill = "#88CCEE")+
   geom_line(data = acan_poo_muscle_n15_me_unscale, aes(y = estimate__), color = "#88CCEE", alpha = .9, lwd = 1) +
  geom_point(data = acan_23_turb_dat_c2, aes(pch = "Surgeonfish", color = "Surgeonfish"), size = 2)+
  geom_point(aes(pch = "Damselfish", color = "Damselfish"), size = 2)+
  scale_color_manual(values = poo_colors, name = "")+
    scale_shape_manual(values = shape, name = "")+
    ylab(expression(Fecal~italic(delta)^15*N)) +
      xlab(expression(Muscle~italic(delta)^15*N)) +
 # scale_fill_manual(values = colors)+
  theme_bw() +
   theme(element_text(size = 12),
     panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.position = "inside",
        legend.position.inside = c(.8, .2))
poo_muscle_n15_plot


##posterior plot-----
 poo_muscle_n15_post_plot<-
ggplot() +
   geom_vline(xintercept=0, lty=2, alpha = .5)+
###Posterior densities for stegastes - n15 
  stat_halfeye(data = as_draws_df(steg_poo_muscle_n15_size_mod_c_no_out_nest), aes(x = b_Muscle_N15_c,  y = 1.1, fill = "Damselfish", color = "Damselfish", pch = "Damselfish"), 
               point_interval=NULL,  slab_alpha = .3) + 
  ##posterior densites for Atri:
  stat_halfeye(data = as_draws_df(acan_poo_muscle_n15_size_mod_c_nest), aes(x = b_Muscle_N15_c,  y = 1, fill = "Surgeonfish", color = "Surgeonfish", pch = "Surgeonfish"), 
               point_interval=NULL,  slab_alpha = .5) + 
  
  ##re-set color scale because outline is throwing off the legend:  
    scale_fill_manual(values = poo_colors, name = "")+
    scale_color_manual(values = poo_colors, name = "")+
    new_scale_color()+
   new_scale_fill()+
  
  #slab outline stegastes:
    stat_halfeye(data = as_draws_df(steg_poo_muscle_n15_size_mod_c_no_out_nest), aes(x = b_Muscle_N15_c,  y = 1.1), point_interval = NULL, slab_fill = NA, outline_bars = TRUE, slab_color = "#332288",   slab_linewidth = .5 ) + 
  
    #slab outline acan:
    stat_halfeye(data = as_draws_df(acan_poo_muscle_n15_size_mod_c_nest), aes(x = b_Muscle_N15_c,  y = 1), point_interval = NULL,  slab_fill = NA, outline_bars = TRUE, slab_color = "#88CCEE",   slab_linewidth = .5 ) + 
  
  
  #intervals acan:
   stat_halfeye(data = as_draws_df(acan_poo_muscle_n15_size_mod_c_nest), aes(x = b_Muscle_N15_c,  y = 1, fill = "Surgeonfish", color = "Surgeonfish"), 
               point_interval=median_hdi, .width=c(.85,.5),  slab_alpha = .0, pch= 17,  point_size = 2 ) + 
  
  ###intervals for stegastes:   
  stat_halfeye(data = as_draws_df(steg_poo_muscle_n15_size_mod_c_no_out_nest), aes(x = b_Muscle_N15_c,  y = 1.1, fill = "Damselfish", color = "Damselfish"), 
               point_interval=median_hdi, .width=c(.85,.5),  slab_alpha = 0,  point_size = 2) + 
  
#now set formatting:
  scale_y_continuous(breaks = NULL)+
       scale_fill_manual(values = poo_colors, name = "", guide = "none")+
  scale_color_manual(values = poo_colors, name = "", guide = "none")+
      scale_shape_manual(values = shape, name = "")+
  ylab("")+
 # xlab(expression(Posterior~effect~of~macroalgal~italic(delta)^15*N~on~poole~italic(delta)^15*N)) +
 xlab("")+
 theme_bw() +
   theme(element_text(size = 12),
         legend.background = element_blank(),
         panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        panel.background = element_blank(),
       plot.background = element_blank(),
        legend.title = element_blank(),
       # legend.position = c(.8, .8),
        legend.position = "none")

poo_muscle_n15_post_plot

###combine and save------
poo_muscle_n15_plot_inset <-
  ggdraw() +
  draw_plot(poo_muscle_n15_plot) +
  draw_plot(poo_muscle_n15_post_plot, x = 0.1, y = .64, width = .45, height = .35)
poo_muscle_n15_plot_inset


#ggsave(plot = poo_muscle_n15_plot_inset, filename = "../outputs/figures/supp_fig_musc_poo_n15.tif", 
#       width  = 1476, height = 1476, units = "px")

```

