---
title: "tetiaroa-fish-nut-vbgf"
output: html_document
date: "2026-05-06"
---

#from reviewer comments, alter growth model to add the δ15N into the growth model, influencing K specifically. Then you would have the explicit influence on the growth rate. Model structure would look something like this: 
#y ~ normal(mu, sigma)
#mu = Linf(1-exp(-k(t-t0))
#k ~ normal(mu_k, sigma_k)
#mu_k = k_intercept + (b * δ15N)
#If δ15N is standardized around zero, it would be reasonable to add an informative prior on k_intercept, Linf, and t0 based on published literature



##load packages
```{r}
library(tidyverse) #for everything

library(cowplot) #for combining plots

#for bayesian modelling and interpreting:
library(brms)
library(tidybayes)
library(emmeans)

library(ggnewscale)

library(jtools)


```


#load data 
```{r}
acan_23_dat<-read.csv("../data/acanthurus_data.csv")%>%
  select(-X)

steg_23_dat<-read.csv("../data/stegastes_data.csv")%>%
  select(-X)


str(acan_23_dat)
str(steg_23_dat)


##center data----
#acanthurus with %c outlier:
acan_23_dat_c<-
  acan_23_dat%>%
  mutate(Muscle_N15_c = base::scale(Muscle_N15, center = TRUE, scale = FALSE),
         Muscle_N_log = log(Muscle_N),
          Muscle_C_log = log(Muscle_C),
         Muscle_CN_log = log(Muscle_CN),
         Poo_N15_c = base::scale(Poo_N15, center = TRUE, scale = FALSE),
         Poo_N_log = log(Poo_N),
         Poo_C_log = log(Poo_C),
         Poo_CN_log = log(Poo_CN),
         HSI_log = log(HSI),
         GSI_log = log(GSI))%>%
  mutate(TL_cm_c = base::scale(TL_cm, center = TRUE, scale = FALSE),
         Age_c = base::scale(Age, center = TRUE, scale = FALSE))

#stegastes, with outlier:
steg_23_dat_c<-
  steg_23_dat%>%
  mutate(Muscle_N15_c = base::scale(Muscle_N15, center = TRUE, scale = FALSE),
         Muscle_N_log = log(Muscle_N),
          Muscle_C_log = log(Muscle_C),
         Muscle_CN_log = log(Muscle_CN),
         Poo_N15_c = base::scale(Poo_N15, center = TRUE, scale = FALSE),
         Poo_N_log = log(Poo_N),
         Poo_C_log = log(Poo_C),
         Poo_CN_log = log(Poo_CN),
         HSI_log = log(HSI),
         GSI_log = log(GSI))%>%
  mutate(TL_cm_c = base::scale(TL_cm, center = TRUE, scale = FALSE),
         Age_c = base::scale(Age, center = TRUE, scale = FALSE))

```
####---without outliers----

##Acanthurus growth----
```{r}
###remove no data for growth and log:----
acan_23_dat_c_gr1<-
  acan_23_dat_c%>%
  filter(Muscle_C<52)%>%
  filter(!is.na(Age))%>%
  mutate(llength = log(TL_cm))%>%
  mutate(Muscle_N15_c = base::scale(Muscle_N15, center = TRUE, scale = FALSE),
          Poo_N15_c = base::scale(Poo_N15, center = TRUE, scale = FALSE))


#use vbgf parameterization from reviewer:---------
#note: results match alternative vbgf parameterization**
#(log coefficients for efficient sampling, easier interpretation)
#mu = Linf(1-exp(-k(t-t0))

#with log: 
prior_vb_acan <- c(
  prior(normal(log(0.2), 0.5), nlpar = "logK", coef = "Intercept"),
  prior(normal(0, 0.5), nlpar = "logK", coef = "Muscle_N15_c"),
  prior(normal(log(100), 1), nlpar = "logLinf"),
  prior(normal(0, 1), nlpar = "t0")
)

vb_model_acan_log_cf1 <- brm(
  bf(
    TL_cm ~ exp(logLinf) * (1 - exp(-exp(logK) * (Age - t0))),
    logK ~ 1 + Muscle_N15_c,
    logLinf ~ 1,
    t0 ~ 1,
    nl = TRUE
  ),
  data = acan_23_dat_c_gr1,
  family = gaussian(),
   prior = prior_vb_acan,
     iter = 3000, warmup = 1000, chains = 4, cores = 4, 
    control = list(adapt_delta = 0.999, max_treedepth=15), 
    sample_prior=TRUE,
     file = "../outputs/brms/vb_model_acan_log_cf1"
)

print(vb_model_acan_log_cf1) ##0 divergent
pp_check(vb_model_acan_log_cf1) #looks good
hypothesis(vb_model_acan_log_cf1, c("logK_Muscle_N15_c>0")) #1**


```


##Stegastes growth----
```{r}
###remove no data for growth and log:----
steg_23_dat_c_gr1<-
  steg_23_dat_c%>%
    filter(Muscle_N15<=14)%>%
  filter(!is.na(Age))%>%
  mutate(llength = log(TL_cm))%>%
  mutate(Muscle_N15_c = base::scale(Muscle_N15, center = TRUE, scale = FALSE),
          Poo_N15_c = base::scale(Poo_N15, center = TRUE, scale = FALSE))



#use vbgf parameterization from reviewer---------
#note: results match alternative vbgf parameterization**
#mu = Linf(1-exp(-k(t-t0))
#with log for better sampling and easier interpretation

prior_vb_steg <- c(
  prior(normal(log(0.2), 0.5), nlpar = "logK", coef = "Intercept"),
  prior(normal(0, 0.5), nlpar = "logK", coef = "Muscle_N15_c"),
  prior(normal(log(100), 1), nlpar = "logLinf"),
  prior(normal(0, 1), nlpar = "t0")
)

vb_model_steg_log_cf1 <- brm(
  bf(
    TL_cm ~ exp(logLinf) * (1 - exp(-exp(logK) * (Age - t0))),
    logK ~ 1 + Muscle_N15_c,
    logLinf ~ 1,
    t0 ~ 1,
    nl = TRUE
  ),
  data = steg_23_dat_c_gr1,
  family = gaussian(),
   prior = prior_vb_steg,
     iter = 3000, warmup = 1000, chains = 4, cores = 4, 
    control = list(adapt_delta = 0.999, max_treedepth=15), 
    sample_prior=TRUE,
     file = "../outputs/brms/vb_model_steg_log_cf1"
)

print(vb_model_steg_log_cf1) ##0 divergent
pp_check(vb_model_steg_log_cf1) #looks good
hypothesis(vb_model_steg_log_cf1, c("logK_Muscle_N15_c>0")) #.
#**So this matches original conclusions - should use this formulation as suggested by R1

```

#repeat growth with fecal N15:
```{r}

#Acanthurus-----
##repeat formula to use with poo n15:----
#with log: 
prior_vb_acan_poo <- c(
  prior(normal(log(0.2), 0.5), nlpar = "logK", coef = "Intercept"),
  prior(normal(0, 0.5), nlpar = "logK", coef = "Poo_N15_c"),
  prior(normal(log(100), 1), nlpar = "logLinf"),
  prior(normal(0, 1), nlpar = "t0")
)

vb_model_acan_log_poo1 <- brm(
  bf(
    TL_cm ~ exp(logLinf) * (1 - exp(-exp(logK) * (Age - t0))),
    logK ~ 1 + Poo_N15_c,
    logLinf ~ 1,
    t0 ~ 1,
    nl = TRUE
  ),
  data = acan_23_dat_c_gr1,
  family = gaussian(),
   prior = prior_vb_acan_poo,
     iter = 3000, warmup = 1000, chains = 4, cores = 4, 
    control = list(adapt_delta = 0.999, max_treedepth=15), 
    sample_prior=TRUE,
     file = "../outputs/brms/vb_model_acan_log_poo1"
)

print(vb_model_acan_log_poo1) ##0 divergent
pp_check(vb_model_acan_log_poo1) #looks good
hypothesis(vb_model_acan_log_poo1, c("logK_Poo_N15_c>0")) #1**



##Stegastes:----------
##repeat formula to use with poo n15:----

#with log: 
prior_vb_steg_poo <- c(
  prior(normal(log(0.2), 0.5), nlpar = "logK", coef = "Intercept"),
  prior(normal(0, 0.5), nlpar = "logK", coef = "Poo_N15_c"),
  prior(normal(log(100), 1), nlpar = "logLinf"),
  prior(normal(0, 1), nlpar = "t0")
)

vb_model_steg_log_poo1 <- brm(
  bf(
    TL_cm ~ exp(logLinf) * (1 - exp(-exp(logK) * (Age - t0))),
    logK ~ 1 + Poo_N15_c,
    logLinf ~ 1,
    t0 ~ 1,
    nl = TRUE
  ),
  data = steg_23_dat_c_gr1,
  family = gaussian(),
   prior = prior_vb_steg_poo,
     iter = 3000, warmup = 1000, chains = 4, cores = 4, 
    control = list(adapt_delta = 0.999, max_treedepth=15), 
    sample_prior=TRUE,
     file = "../outputs/brms/vb_model_steg_log_poo1"
)

print(vb_model_steg_log_poo1) ##0 divergent
pp_check(vb_model_steg_log_poo1) #looks good
hypothesis(vb_model_steg_log_poo1, c("logK_Poo_N15_c>0")) 

```

###extract results as change in growth rate:
```{r}
#stegastes:-----
vb_model_steg_log_cf1%>%
  spread_draws(b_logK_Muscle_N15_c)%>%
  median_hdi(exp(b_logK_Muscle_N15_c))
#1.024098	0.8987081	1.153869	
1-0.8987 #lower bound = -10.13%

#poo
vb_model_steg_log_poo1%>%
  spread_draws(b_logK_Poo_N15_c)%>%
  median_hdi(exp(b_logK_Poo_N15_c))
#0.9708056	0.9046062	1.035053	

vb_model_steg_log_poo1%>%
  spread_draws(b_logK_Poo_N15_c)%>%
  median_hdi(1-exp(b_logK_Poo_N15_c))
#0.02919437	-0.03505295	0.09539376	


#acanthurus:-----
vb_model_acan_log_cf1%>%
  spread_draws(b_logK_Muscle_N15_c)%>%
  median_hdi(exp(b_logK_Muscle_N15_c))
#1.057262	1.012187	1.106589		

#so 5.72% increase (95% HPDI: 1.2 - 10.7%)


#poo
vb_model_acan_log_poo1%>%
  spread_draws(b_logK_Poo_N15_c)%>%
  median_hdi(exp(b_logK_Poo_N15_c))
#1.062888	1.021209	1.10845	



```


##FIGURES - GROWTH CURVES - MUSCLE N15-----------
```{r}
steg_growth_me<- conditional_effects(vb_model_steg_log_cf1, plot = FALSE, prob = 0.85)[[1]]
steg_growth_me



acan_growth_me<- conditional_effects(vb_model_acan_log_cf1, plot = FALSE, prob = 0.85)[[1]]
acan_growth_me


###by muscle n15:------
musc_colors <- c("Damselfish" = "#117733", "Surgeonfish" = "#44AA99")
shape<-c("Damselfish" = 19, "Surgeonfish" = 17)


steg_growth_curve_muscle<-
steg_23_dat_c_gr1%>%
  ggplot(aes(x = Age, y = TL_cm))+
   geom_ribbon(data = steg_growth_me, aes(y = estimate__,  ymin = lower__, ymax=upper__), alpha = .2, fill = "#117733")+
   geom_line(data = steg_growth_me, aes(y = estimate__), color = "#117733", alpha = .9, lwd = 1) +
  geom_point(aes(pch = "Damselfish", color = Muscle_N15, fill = Muscle_N15), size = 2)+
  scale_fill_viridis_c(name = expression("Muscle " * delta^15 * "N"),option = "mako")+
    scale_color_viridis_c(name = expression("Muscle " * delta^15 * "N"), option = "mako")+
    scale_shape_manual(values = shape, name = "", guide = "none")+
    ylab("Damselfish length (cm)") +
      xlab("Damselfish age (years)") +
 # scale_fill_manual(values = colors)+
  theme_bw() +
   theme(element_text(size = 12),
         panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
       # legend.title = element_blank(),
        legend.background = element_blank(),
        legend.position = "inside",
        legend.position.inside = c(.8, .32))

steg_growth_curve_muscle





acan_growth_curve_muscle<-
acan_23_dat_c_gr1%>%
  ggplot(aes(x = Age, y = TL_cm))+
   geom_ribbon(data = acan_growth_me, aes(y = estimate__,  ymin = lower__, ymax=upper__), alpha = .2, fill = "#44AA99")+
   geom_line(data = acan_growth_me, aes(y = estimate__), color = "#44AA99", alpha = .9, lwd = 1) +
  geom_point(aes(pch = "Surgeonfish", color = Muscle_N15, fill = Muscle_N15), size = 2)+
  scale_fill_viridis_c(name = expression("Muscle " * delta^15 * "N"), option = "mako")+
    scale_color_viridis_c(name = expression("Muscle " * delta^15 * "N"),option = "mako")+
   scale_shape_manual(values = shape, name = "", guide = "none")+
    ylab("Surgeonfish length (cm)") +
      xlab("Surgeonfish age (years)") +
 # scale_fill_manual(values = colors)+
  theme_bw() +
   theme(element_text(size=12),
         panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
       # legend.title = element_blank(),
        legend.background = element_blank(),
        legend.position = "inside",
        legend.position.inside = c(.8, .32))

acan_growth_curve_muscle


```




##FIGURES - GROWTH CURVES - FECAL N15-----------
```{r}
steg_growth_me_poo<- conditional_effects(vb_model_steg_log_poo1, plot = FALSE, prob = 0.85)[[1]]
steg_growth_me_poo


acan_growth_me_poo<- conditional_effects(vb_model_acan_log_poo1, plot = FALSE, prob = 0.85)[[1]]
acan_growth_me_poo



###by muscle n15:------
musc_colors <- c("Damselfish" = "#117733", "Surgeonfish" = "#44AA99")
shape<-c("Damselfish" = 19, "Surgeonfish" = 17)


steg_growth_curve_poo<-
steg_23_dat_c_gr1%>%
  ggplot(aes(x = Age, y = TL_cm))+
   geom_ribbon(data = steg_growth_me_poo, aes(y = estimate__,  ymin = lower__, ymax=upper__), alpha = .2, fill = "#332288")+
   geom_line(data = steg_growth_me_poo, aes(y = estimate__), color = "#332288", alpha = .9, lwd = 1) +
  geom_point(aes(pch = "Damselfish", color = Poo_N15, fill = Poo_N15), size = 2)+
  scale_fill_viridis_c(name = expression("Fecal " * delta^15 * "N"),option = "mako")+
    scale_color_viridis_c(name = expression("Fecal " * delta^15 * "N"), option = "mako")+
    scale_shape_manual(values = shape, name = "", guide = "none")+
    ylab("Damselfish length (cm)") +
      xlab("Damselfish age (years)") +
 # scale_fill_manual(values = colors)+
  theme_bw() +
   theme(element_text(size = 12),
         panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
       # legend.title = element_blank(),
        legend.background = element_blank(),
        legend.position = "inside",
        legend.position.inside = c(.8, .32))

steg_growth_curve_poo





acan_growth_curve_poo<-
acan_23_dat_c_gr1%>%
  ggplot(aes(x = Age, y = TL_cm))+
   geom_ribbon(data = acan_growth_me_poo, aes(y = estimate__,  ymin = lower__, ymax=upper__), alpha = .2, fill = "#88CCEE")+
   geom_line(data = acan_growth_me_poo, aes(y = estimate__), color = "#88CCEE", alpha = .9, lwd = 1) +
  geom_point(aes(pch = "Surgeonfish", color = Poo_N15, fill = Poo_N15), size = 2)+
  scale_fill_viridis_c(name = expression("Fecal " * delta^15 * "N"), option = "mako")+
    scale_color_viridis_c(name = expression("Fecal " * delta^15 * "N"),option = "mako")+
   scale_shape_manual(values = shape, name = "", guide = "none")+
    ylab("Surgeonfish length (cm)") +
      xlab("Surgeonfish age (years)") +
 # scale_fill_manual(values = colors)+
  theme_bw() +
   theme(element_text(size=12),
         panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
       # legend.title = element_blank(),
        legend.background = element_blank(),
        legend.position = "inside",
        legend.position.inside = c(.8, .32))

acan_growth_curve_poo


```


##Posterior Plots for VBGF Muscle effects on K
```{r}

#plot stegastes and acanthurus together: GROWTH, musc------
musc_colors <- c("Damselfish" = "#117733", "Surgeonfish" = "#44AA99")



growth_musc_posterior_plot<-
ggplot() +
   geom_vline(xintercept=1, lty=2, alpha = .5)+
  
###Posterior densities for stegastes - n, c, c:n:   
  stat_halfeye(data = as_draws_df(vb_model_steg_log_cf1), aes(x = exp(b_logK_Muscle_N15_c),  y = 1.1, fill = "Damselfish", color = "Damselfish"), point_interval = NULL, slab_alpha = .3) + 
  
  ##posterior densities for Atri:
  stat_halfeye(data = as_draws_df(vb_model_acan_log_cf1), aes(x = exp(b_logK_Muscle_N15_c),  y = 1, fill = "Surgeonfish", color = "Surgeonfish"), point_interval = NULL, slab_alpha = .3) + 

  ##re-set color scale because outline is throwing off the legend:  
    scale_fill_manual(values = musc_colors, name = "")+
    scale_color_manual(values = musc_colors, name = "")+
    new_scale_color()+
   new_scale_fill()+
  
  ###Posterior densities for stegastes - OUTLINES:   
  stat_halfeye(data = as_draws_df(vb_model_steg_log_cf1), aes(x = exp(b_logK_Muscle_N15_c),  y = 1.1), point_interval = NULL, slab_fill = NA, outline_bars = TRUE, slab_color = "#117733",   slab_linewidth = .5 ) + 
  
  ##posterior densites for Atri OUTLINES:
  stat_halfeye(data = as_draws_df(vb_model_acan_log_cf1), aes(x = exp(b_logK_Muscle_N15_c),  y = 1),   point_interval = NULL,   slab_fill = NA, outline_bars = TRUE, slab_color = "#44AA99",   slab_linewidth = .5 ) + 

##intervals for Atri:
     stat_halfeye(data = as_draws_df(vb_model_acan_log_cf1), aes(x = exp(b_logK_Muscle_N15_c),  y = 1, fill = "Surgeonfish", color = "Surgeonfish"), 
               point_interval=median_hdi, .width=c(.85,.5),  slab_alpha = .0, pch= 17) + 
  
  ###intervals for stegastes:   
  stat_halfeye(data = as_draws_df(vb_model_steg_log_cf1), aes(x = exp(b_logK_Muscle_N15_c),  y =1.1, fill = "Damselfish", color = "Damselfish"), 
               point_interval=median_hdi, .width=c(.85,.5),  slab_alpha = 0) + 
  
#now set formatting:
  scale_y_continuous(labels = c(""), breaks = c(1))+
  scale_fill_manual(values = musc_colors, name = "", guide = "none")+
  scale_color_manual(values = musc_colors, name = "", guide = "none")+
  ylab("")+
  xlab("Multiplicative effect on growth (K)")+
 theme_bw() +
   theme(element_text(size=12),
         panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
         legend.background = element_blank(),
       legend.title = element_blank(),
        legend.position = c(.8, .8))

growth_musc_posterior_plot





  
#plot stegastes and acanthurus together: GROWTH------
poo_colors <- c("Damselfish" = "#332288", "Surgeonfish" = "#88CCEE")

growth_poo_posterior_plot<-
ggplot() +
   geom_vline(xintercept=1, lty=2, alpha = .5)+
  
###Posterior densities for stegastes - n, c, c:n:   
  stat_halfeye(data = as_draws_df(vb_model_steg_log_poo1), aes(x = exp(b_logK_Poo_N15_c),  y = 1.1, fill = "Damselfish", color = "Damselfish"), point_interval = NULL, slab_alpha = .3) + 
  
  ##posterior densities for Atri:
  stat_halfeye(data = as_draws_df(vb_model_acan_log_poo1), aes(x = exp(b_logK_Poo_N15_c),  y = 1, fill = "Surgeonfish", color = "Surgeonfish"), point_interval = NULL, slab_alpha = .5) + 

  ##re-set color scale because outline is throwing off the legend:  
    scale_fill_manual(values = poo_colors, name = "")+
    scale_color_manual(values = poo_colors, name = "")+
    new_scale_color()+
   new_scale_fill()+
  
  ###Posterior densities for stegastes - OUTLINES:   
  stat_halfeye(data = as_draws_df(vb_model_steg_log_poo1), aes(x = exp(b_logK_Poo_N15_c),  y = 1.1), point_interval = NULL, slab_fill = NA, outline_bars = TRUE, slab_color = "#332288",   slab_linewidth = .5 ) + 
  
  ##posterior densites for Atri OUTLINES:
  stat_halfeye(data = as_draws_df(vb_model_acan_log_poo1), aes(x = exp(b_logK_Poo_N15_c),  y = 1),   point_interval = NULL,   slab_fill = NA, outline_bars = TRUE, slab_color = "#88CCEE",   slab_linewidth = .5 ) + 

##intervals for Atri:
     stat_halfeye(data = as_draws_df(vb_model_acan_log_poo1), aes(x = exp(b_logK_Poo_N15_c),  y = 1, fill = "Surgeonfish", color = "Surgeonfish"), 
               point_interval=median_hdi, .width=c(.85,.5),  slab_alpha = .0, pch= 17) + 
  
  ###intervals for stegastes:   
  stat_halfeye(data = as_draws_df(vb_model_steg_log_poo1), aes(x = exp(b_logK_Poo_N15_c),  y =1.1, fill = "Damselfish", color = "Damselfish"), 
               point_interval=median_hdi, .width=c(.85,.5),  slab_alpha = 0) + 
  
#now set formatting:
  scale_y_continuous(labels = c(""), breaks = c(1))+
 # scale_x_continuous(limits = c(-.10, .10))+
  scale_fill_manual(values = poo_colors, name = "", guide = "none")+
  scale_color_manual(values = poo_colors, name = "", guide = "none")+
  ylab("")+
  xlab("Multiplicative effect on growth (K)")+
 theme_bw() +
   theme(element_text(size=12),
         panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
         legend.background = element_blank(),
       legend.title = element_blank(),
        legend.position = c(.8, .88))
growth_poo_posterior_plot


```









####--------------------repeat with outliers--------------------

##Acanthurus growth----
```{r}
###remove no data for growth and log:----
acan_23_dat_c_gr<-
  acan_23_dat_c%>%
  filter(!is.na(Age))%>%
  mutate(llength = log(TL_cm))%>%
  mutate(Muscle_N15_c = base::scale(Muscle_N15, center = TRUE, scale = FALSE),
          Poo_N15_c = base::scale(Poo_N15, center = TRUE, scale = FALSE))


#use vbgf parameterization from reviewer:---------
#note: results match alternative vbgf parameterization**
#(log coefficients for efficient sampling, easier interpretation)
#mu = Linf(1-exp(-k(t-t0))

#with log: 
prior_vb_acan <- c(
  prior(normal(log(0.2), 0.5), nlpar = "logK", coef = "Intercept"),
  prior(normal(0, 0.5), nlpar = "logK", coef = "Muscle_N15_c"),
  prior(normal(log(100), 1), nlpar = "logLinf"),
  prior(normal(0, 1), nlpar = "t0")
)

vb_model_acan_log_cf <- brm(
  bf(
    TL_cm ~ exp(logLinf) * (1 - exp(-exp(logK) * (Age - t0))),
    logK ~ 1 + Muscle_N15_c,
    logLinf ~ 1,
    t0 ~ 1,
    nl = TRUE
  ),
  data = acan_23_dat_c_gr,
  family = gaussian(),
   prior = prior_vb_acan,
     iter = 3000, warmup = 1000, chains = 4, cores = 4, 
    control = list(adapt_delta = 0.999, max_treedepth=15), 
    sample_prior=TRUE,
     file = "../outputs/brms/vb_model_acan_log_cf"
)

print(vb_model_acan_log_cf) ##0 divergent
pp_check(vb_model_acan_log_cf) #looks good
hypothesis(vb_model_acan_log_cf, c("logK_Muscle_N15_c>0")) #1**


```


##Stegastes growth----
```{r}
###remove no data for growth and log:----
steg_23_dat_c_gr<-
  steg_23_dat_c%>%
  filter(!is.na(Age))%>%
  mutate(llength = log(TL_cm))%>%
  mutate(Muscle_N15_c = base::scale(Muscle_N15, center = TRUE, scale = FALSE),
          Poo_N15_c = base::scale(Poo_N15, center = TRUE, scale = FALSE))



#use vbgf parameterization from reviewer---------
#note: results match alternative vbgf parameterization**
#mu = Linf(1-exp(-k(t-t0))
#with log for better sampling and easier interpretation

prior_vb_steg <- c(
  prior(normal(log(0.2), 0.5), nlpar = "logK", coef = "Intercept"),
  prior(normal(0, 0.5), nlpar = "logK", coef = "Muscle_N15_c"),
  prior(normal(log(100), 1), nlpar = "logLinf"),
  prior(normal(0, 1), nlpar = "t0")
)

vb_model_steg_log_cf <- brm(
  bf(
    TL_cm ~ exp(logLinf) * (1 - exp(-exp(logK) * (Age - t0))),
    logK ~ 1 + Muscle_N15_c,
    logLinf ~ 1,
    t0 ~ 1,
    nl = TRUE
  ),
  data = steg_23_dat_c_gr,
  family = gaussian(),
   prior = prior_vb_steg,
     iter = 3000, warmup = 1000, chains = 4, cores = 4, 
    control = list(adapt_delta = 0.999, max_treedepth=15), 
    sample_prior=TRUE,
     file = "../outputs/brms/vb_model_steg_log_cf"
)

print(vb_model_steg_log_cf) ##0 divergent
pp_check(vb_model_steg_log_cf) #looks good
hypothesis(vb_model_steg_log_cf, c("logK_Muscle_N15_c>0")) #.3
#**So this matches original conclusions - should use this formulation as suggested by R1

```

#repeat growth with fecal N15:
```{r}

#Acanthurus-----
##repeat formula to use with poo n15:----
#with log: 
prior_vb_acan_poo <- c(
  prior(normal(log(0.2), 0.5), nlpar = "logK", coef = "Intercept"),
  prior(normal(0, 0.5), nlpar = "logK", coef = "Poo_N15_c"),
  prior(normal(log(100), 1), nlpar = "logLinf"),
  prior(normal(0, 1), nlpar = "t0")
)

vb_model_acan_log_poo <- brm(
  bf(
    TL_cm ~ exp(logLinf) * (1 - exp(-exp(logK) * (Age - t0))),
    logK ~ 1 + Poo_N15_c,
    logLinf ~ 1,
    t0 ~ 1,
    nl = TRUE
  ),
  data = acan_23_dat_c_gr,
  family = gaussian(),
   prior = prior_vb_acan_poo,
     iter = 3000, warmup = 1000, chains = 4, cores = 4, 
    control = list(adapt_delta = 0.999, max_treedepth=15), 
    sample_prior=TRUE,
     file = "../outputs/brms/vb_model_acan_log_poo"
)

print(vb_model_acan_log_poo) ##0 divergent
pp_check(vb_model_acan_log_poo) #looks good
hypothesis(vb_model_acan_log_poo, c("logK_Poo_N15_c>0")) #1**



##Stegastes:----------
##repeat formula to use with poo n15:----

#with log: 
prior_vb_steg_poo <- c(
  prior(normal(log(0.2), 0.5), nlpar = "logK", coef = "Intercept"),
  prior(normal(0, 0.5), nlpar = "logK", coef = "Poo_N15_c"),
  prior(normal(log(100), 1), nlpar = "logLinf"),
  prior(normal(0, 1), nlpar = "t0")
)

vb_model_steg_log_poo <- brm(
  bf(
    TL_cm ~ exp(logLinf) * (1 - exp(-exp(logK) * (Age - t0))),
    logK ~ 1 + Poo_N15_c,
    logLinf ~ 1,
    t0 ~ 1,
    nl = TRUE
  ),
  data = steg_23_dat_c_gr,
  family = gaussian(),
   prior = prior_vb_steg_poo,
     iter = 3000, warmup = 1000, chains = 4, cores = 4, 
    control = list(adapt_delta = 0.999, max_treedepth=15), 
    sample_prior=TRUE,
     file = "../outputs/brms/vb_model_steg_log_poo"
)

print(vb_model_steg_log_poo) ##0 divergent
pp_check(vb_model_steg_log_poo) #looks good
hypothesis(vb_model_steg_log_poo, c("logK_Poo_N15_c>0")) #.45

```

###extract results as change in growth rate:
```{r}
#stegastes:-----
vb_model_steg_log_cf%>%
  spread_draws(b_logK_Muscle_N15_c)%>%
  median_hdi(exp(b_logK_Muscle_N15_c))
#0.9805421	0.9034925	1.060041	

vb_model_steg_log_cf%>%
  spread_draws(b_logK_Muscle_N15_c)%>%
  median_hdi(1-exp(b_logK_Muscle_N15_c))
#0.01945789	-0.0600406	0.0965075
#so decrease of 2% growth, between - 9.6% and + 6% 


#poo
vb_model_steg_log_poo%>%
  spread_draws(b_logK_Poo_N15_c)%>%
  median_hdi(exp(b_logK_Poo_N15_c))
#0.9702768	0.9048772	1.031407	

vb_model_steg_log_poo%>%
  spread_draws(b_logK_Poo_N15_c)%>%
  median_hdi(1-exp(b_logK_Poo_N15_c))
#0.02972317	-0.0314067	0.0951228	


#acanthurus:-----
vb_model_acan_log_cf%>%
  spread_draws(b_logK_Muscle_N15_c)%>%
  median_hdi(exp(b_logK_Muscle_N15_c))
#1.056627	1.014759	1.104158	

#so 5.66% increase (95% HPDI: 1.5 - 10.4%)


#poo
vb_model_acan_log_poo%>%
  spread_draws(b_logK_Poo_N15_c)%>%
  median_hdi(exp(b_logK_Poo_N15_c))
#1.061958	1.022548	1.107082	



```